---
title: "3rd Markdown Assignment"
author: "Gian Carlo Fernandez, John Kyle LLuz, Adrian Enrico Rodriguez, Iris Salangad"
date: "7/31/2021"
output:
  html_document:
    highlight: pygments
    theme: default
---

# An Effort to Lower Electricity Bill in University Building by Automatic Lighting Switches Application {.tabset .tabset-pills}

Martini Martini, Indra Riyanto, Adiyarta Krisna, M. Suparmoko

## Introduction

### **Introduction**

-----

As of writing this paper, the world is in hiatus from fully experiencing the world outside their homes.  In the midst of the COVID-19 pandemic, part of mitigating infection is the limitation of physical interactions among human beings.  With that, one solution set by the governments across various nations is putting their countries in quarantine.  While this certainly helps prevent the spread of the virus, there are other accompanying deficiencies in this solution beyond the virus.  One of which is the rise in household utility bills such as electricity.  During the pandemic, Filipino families have relied on electrically powered appliances such as air conditioners, televisions, and the like for comfort and entertainment.  With that, they also result in higher, sometimes unprecedented, electricity charges [1].

<br>

Given this timely issue, solutions should be explored and implemented surrounding concepts of energy reduction and cost efficiency.  With that, the group came across an Indonesian academic article written by Martini et al. which tackles a simple yet impactful solution to  reducing the cost of electrical bills.  They identified that one of the most overlooked factors to heightened electricity bill prices is the constant usage of light bulbs and lamps.  Using fundamental concepts of electronics and programming, the researchers were able to test automatic light switches (sensor-based) against manual, traditional light switches in public restrooms as these are places wherein light is left on for long periods of time - therefore implying larger energy consumption and cost.
	
<br>

The study conducted by Martini et al. included 13 different samples depending on duration wherein the following essential data were obtained:  energy consumption with the sensor, energy consumption without the sensor, cost in Indonesian Rupiah (Rp) with the sensor, and the cost in Rp without the sensor.  However, the group ultimately decided to focus on energy consumption with the sensor as well as energy consumption without the sensor since conclusions regarding cost can immediately be drawn from these sets of data.  These were obtained by determining how much electrical power in kilowatt hour (kWh) was consumed at various fixed periods of time and comparing data with the sensor and with its absence.  In conclusion, the group would like to determine whether the application of sensor-based light switches can help decrease electricity consumption.

<br><br><br>

## Methodology

### **Methodology**

-----

In this paper, an infrared-based sensor namely Passive Infrared Receiver or PIR is used to detect body movements present. Based on its name, PIR is a passive type of sensor meaning by itself, it does not emit infrared radiations. With this distinct quality, PIR is the suitable device to use in this study as the detected heat radiation is solely caused by human presence and body movements, creating a more controlled environment guaranteed from external errors.

<br>

With the goal to identify whether the sensors will decrease power consumption and consequently the cost, the Indonesian authors used the simplest way to obtain results. The plan was to compare the Electrical power consumed (in kWh) before and after the sensors’ installations. The experiment room to be used was a public restroom in their building, since restrooms are places where people come and go, making it an appropriate set-up for the experiment. The authors then installed the sensors on the electrical appliances (lamps and exhaust fans) to obtain a wide area of the room, and the Electrical Power Consumption Meter for the facilitation of data measurement. After measuring the power consumption every 7 hours for 13 times, the sensors and program were now activated and the second half of the reading and measuring proceeded.

<br>

We, the researchers, will conduct a hypothesis test and the next step would be identifying the parameters. The parameters to be calculated are the means and standard deviations of both variables. The sample of both variables are the same which is 13 and lastly, we will use a 5% confidence interval for this hypothesis test.

:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 10px;"}

:::: {}

#### **With Sensor**

##### Mean

$$
  \overline{x} = 11.6
$$

##### Standard Deviation

$$
  \sigma=\sqrt{(\frac{1}{n-1})\sum_{i=1}^{n}{(x_i - \bar{x})^2}}
$$

$$
  \sigma=\sqrt{\frac{488.54016892308}{13-1}}
$$

$$
  \sigma=\sqrt{40.71168074359}
$$
$$
  	\sigma=6.3805705656775 ≈ 6.4
$$
:::

:::{}

#### **Without Sensor**

##### Mean

$$
  \overline{x} = 27.9
$$

##### Standard Deviation

$$
  \sigma=\sqrt{(\frac{1}{n-1})\sum_{i=1}^{n}{(x_i - \bar{x})^2}}
$$

$$
  \sigma=\sqrt{\frac{3895.2822449231}{13-1}}
$$

$$
  \sigma=\sqrt{324.60685374359}
$$
$$
  	\sigma=18.016849162481 ≈ 18
$$
:::

::::

<br><br><br>

## Results

### **Results**

-----

### **Using the 7-Step Approach**

#### **Step 1: Parameter of Interest**
We are interested in $\mu_a$ and $\mu_b$, specifically the difference between the energy consumption in kilowatt hours of using the sensor and without the sensor. <br><br>


#### **Step 2: Stating Null Hypothesis**
The null hypothesis would be as follows $H_0 : \mu_A = \mu_b$ saying that there is no significant difference between the energy consumption with the sensor and without it.<br><br>

#### **Step 3: Stating Alternative Hypothesis**
The alternative hypothesis would be as follows $H_1 : \mu_A < \mu_B$ saying that the energy consumption without the sensor would be significantly greater than with the use of the sensor..<br><br>

#### **Step 4: Determining Appropriate Test Statistic**
Since the mean and standard deviation are known (refer to the Methodology section), and the sample is less than 30, then the appropriate test statistic is defined by the formula: 

$$
  t_0 = \frac{\overline{x}_A-\overline{x}_B}{\sqrt{(\frac{s^2_A}{n_A}}+\frac{s^2_B}{n_B})}
$$
<br><br>

#### **Step 5: Reject $H_o$ if**
Reject $H_0$ if the p-value is less than $0.05$

<br><br>
*Calculating the Degree of Freedom*

$$
  D_f = \frac{((\frac{\sigma_a^2}{n_a})+(\frac{\sigma_b^2}{n_b}))^2}{\frac{(\frac{\sigma_a^2}{n_a})^2}{n_a-1}+\frac{(\frac{\sigma_b^2}{n_b})^2}{n_b-1}}
$$

$$
  D_f = \frac{((\frac{6.4^2}{13})+(\frac{18^2}{13}))^2}{\frac{(\frac{6.4^2}{13})^2}{12}+\frac{(\frac{18^2}{13})^2}{12}}
$$

$$
  D_f  = \frac{788.1408379}{0.8272788955+51.76331361}
$$

$$
  D_f  = 14.98634642
\\
  D_f  = 14.99
$$

<br><br>

#### **Step 6: Computations**

$$
 t_0 = \frac{11.6-27.9}{\sqrt{(\frac{6.4^2}{13}}+\frac{18^2}{13})}
$$

$$
  t_0 = -3.078356393
$$

<br> 

We then find the probability of $P(t\ge -3.08)$ by first determining the degrees of freedom which was done in step 5.  Then, we can proceed by using the R function: pt(t, df) to determine this probability then compare it to our level of significance which is $\alpha = 0.05$

```{r}
  pt(-3.078356393, 14.99)
```
<br>
Therefore, the **probability of $P(t\ge -3.08)$ is approximately 0.004.**<br><br>

#### **Step 7: Conclusion** 
Since  **0.004 is significantly less than 0.05**, we reject the null hypothesis. Therefore, we can come to a conclusion that the energy consumption without the use of a sensor is significantly greater than when using a sensor.

-----

:::: {style="display: grid; grid-template-columns: 1fr 1fr; grid-column-gap: 15px;"}

:::: {}




```{r, echo= FALSE, fig.width = 5, fig.height = 3}
df1 <- data.frame(  
                    n             = 1:13,
                    Duration      = c(1,7,14,21,28,35,42,49,56,63,70,77,84),
                    With_Sensors  = c(0.504,2.711,5.058,7.158,8.890,10.622,12.264,13.816,15.278,16.651,17.933,19.126,20.229)
                    
                  )

knitr::kable(df1, caption = '**Electrical Power w/o Sensors**' )




```





```{r, echo= FALSE, fig.width = 5, fig.height = 3}
y = c(1,7,14,21,28,35,42,49,56,63,70,77,84)
x = c(0.504,2.711,5.058,7.158,8.890,10.622,12.264,13.816,15.278,16.651,17.933,19.126,20.229)

plot(
     x~y,
     main = "Energy Consumption W/ Sensors",
     xlab = "Duration (Hours)",
     ylab = "Electrical Power Consumption (kWh)",
     cex  = 1,
     ylim = c(0, 60),
     col  = "red",
     pch  = 21,  
     bg   = "red"
    )

lines(
      x~y,
      bg="red"
     )

line=lm(x~y)
abline(line, col="blue")


```

:::

:::{}



```{r, echo= FALSE, fig.width = 5, fig.height = 3}


df2 <- data.frame(  
                    n                  = 1:13,
                    Duration           = c(1,7,14,21,28,35,42,49,56,63,70,77,84),
                    Without_Sensors    = c(0.664,4.648,9.296,13.944,18.592,23.24,27.888,32.536,37.184,41.832,46.48,51.128,55.776)
                  )
knitr::kable(df2, caption = '**Electrical Power w/o Sensors**' )

```


```{r, echo= FALSE, fig.width = 5, fig.height = 3}
y = c(1,7,14,21,28,35,42,49,56,63,70,77,84)
x = c(0.664,4.648,9.296,13.944,18.592,23.24,27.888,32.536,37.184,41.832,46.48,51.128,55.776)



plot(
     x~y,
     main = "Energy Consumption WITHOUT Sensors",
     xlab = "Duration (Hours)",
     ylab = "Electrical Power (kWh)",
     cex  = 1,
     ylim = c(0, 60),
     col  = "blue",
     pch  = 21,  
     bg   = "blue")

lines(
      x~y,
      bg ="red"
     )

line=lm(x~y)
abline(line, col="red")
```

:::

::::

<br><br>
**Comparison Based on the % of Reduction**


```{r, echo= FALSE}

x = c(0.504,2.711,5.058,7.158,8.890,10.622,12.264,13.816,15.278,16.651,17.933,19.126,20.229)
y = c(0.664,4.648,9.296,13.944,18.592,23.24,27.888,32.536,37.184,41.832,46.48,51.128,55.776)
a = c(0.504,2.711,5.058,7.158,8.890,10.622,12.264,13.816,15.278,16.651,17.933,19.126,20.229)
b = c(0.664,4.648,9.296,13.944,18.592,23.24,27.888,32.536,37.184,41.832,46.48,51.128,55.776)
 
 
test  = a/b
test2 = 1-test
test3 = test2*100


df3 <- data.frame(  
                    x = c(0.504,2.711,5.058,7.158,8.890,10.622,12.264,13.816,15.278,16.651,17.933,19.126,20.229),
                    y = c(0.664,4.648,9.296,13.944,18.592,23.24,27.888,32.536,37.184,41.832,46.48,51.128,55.776),
                    test3
                   )
knitr::kable(df3, caption = '**Table 2**' )

 
```

<center>
```{r, echo= FALSE}

plot(
     test3~y,
     xlab = "duration",
     ylab = "Energy Reduction (%)",
     main = "Energy Reduction per week ",
     cex  = 1,
     ylim = c(0, 65),
     col  = "blue",
     pch  = 21,  
     bg   = "blue"
    )

lines(
      test3~y,
      bg = "blue"
     )

line=lm(test3~y)
abline(line, col="red")

```
</center>


## Discussion and Conclusion

### **Discussion**

-----

Eight 23W lights and six 80W exhaust fans were among the electric equipment placed in the experiment room.These equipment operated daily from 7:00 to 21:00, which consisted of 14 hours per day. Up to 84 hours of operation, measurements are taken every 7 hours. The 84 hours of operation also equated to one 6-day week. Without the usage of motion sensors, total electric power consumption was 55,576 kWh. After 84 hours of operation with the usage of motion sensors, the total electric power consumption reduced to 20.229 kWh. 


According to the first two tables and plots, the consumption has been reduced to half of what it was before after 28 hours of operation. After 84 hours of operation, the reduction reached 63.73%. With these two figures, we can conclude the energy reduction per week. 


### **Conclusion**

-----

According to the results that were found during the testing and experiment, there were still insignificance in the first hours of cost savings. However, the savings had increased considerably to over 60% overtime after one week. According to this report, it is significantly shown that longer duration of operation hours leads to higher energy reduction. 
 

## References

### **References**

-----

<ol>
<li> H. A. Fernandez, “As power Bills surge amid Covid-19, WILL PROSUMERS be the philippines' next big Energy trend?,” Eco, 06-Oct-2020. 
    [Online]. Available: https://www.eco-business.com/news/as-power-bills-surge-amid-covid-19-will-prosumers-be-the-philippines-next-big-energy-trend/. [Accessed: 31-Jul-2021]. </li>
<br>
<li> M. Martini, I. Riyanto, A. Krisna, and M. Suparmoko, An Effort to Lower Electricity Bill in University Building by Automatic Lighting Switches Application, Aug. 2017. [Online]. Available: https://www.researchgate.net/publication/323401202_An_Effort_to_Lower_Electricity_Bill_in_University_Building_by_Automatic_Lighting_Switches_Applicatio. [Accessed: 30-July-2021]. </li>
</ol>